Relationships in the extremes and their influence on competition and coexistence

### 2021-07-14 paper/Paper.Rnw
worked on storage effect section

paragraph to inuitively explain storage effects
We emphasize that although this paper focuses on storage effects, it is still a paper generally about the importance of asymmetrical tail associations for coexistence because we do consider whether they are important for other mechanisms of modern coexistence theory, though we quickly realize their importance is solely for storage effects

>>>>

For clarification, we explain the how storage effects operate in maintaining biodiversity and the conditions that are required for it to do so.
We emphasize that although this paper focuses on storage effects, it is still a paper generally about the importance of ATAs for coexistence because we do consider whether they are important for other mechanisms of modern coexistence theory, though we quickly realize their importance is solely for storage effects. 
Storage effects allow for species to fluctuate over time while escaping extinction. In order for storage effect to be a functioning mechanism in coexistence populations must fluctuate differently in resonse to environmental fluctuations, there must be a relationship between envrionmental responses and competition, and there must variation in responses at different life history stages. In a simple two species system, differences in environmental response allows for one species to grow to high densities while the other is very low. Competition is positively related to environment for the high density species (species A), stabalizing its growth. Conversely, competition is negatively/less positively?/more negative? related to environment for the low density species (species B), leading to large population growth rate fluctuations in both directions. At first glance, this may seem like a scenario for extiction of species B, but it can, in fact, be at an advantage due to the differences in life history stages. Different responses at different stages of life buffer the species against extinction by limiting negative growth rates, but not positive ones. Buffering against negative growth rates can be seen in insensitive adults or dormant seeds that persist even when environmental response amoung others in the population is low (Chesson et al 2012). Thus, higher fluctuation in growth rate can lead to a higher long term mean growth rate. In this paper, we investigate the consequences of having ATAs in the relationship between environmental fluctuations and competitive pressure. More specifically, we answer: Does having higher association in a tail end of the EC relationship, while maintaining overall association, change the contribution of storage effect?
